%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}

\begin{cvpubs}

    \cvpub{\textbf{Aktepe, S.C.} \&  Özge, D. (March 2023). Children can interpret counterfactual conditionals incrementally using morpho-syntactic cues, METU Workshop on Conditional and Causal Reasoning, Muğla, Turkey.}
    
    %\cvpub{\textbf{Aktepe, S.C.} \& Özge, D. (November 2022). Children can interpret counterfactual conditionals incrementally using morpho-syntactic cues, The 47th Boston University Conference on Language Development, Boston, Massachusetts, USA. \textit{(Accepted but had to be retracted due to long visa waiting times of U.S. Embassy of Turkey)}}
    
    \cvpub{\textbf{Aktepe, S.C.} \& Yet, B. (July 2022). Learning unnatural language quantifiers, 44th Annual Meeting of the Cognitive Science, Toronto, Canada.}
    
    \cvpub{\textbf{Aktepe, S.C.} \& Özge, D. (May 2022). Children’s incremental processing of counterfactual morphosyntax tested via VWP, 8th International Symposium on Brain and Cognitive Science, Koç University, İstanbul, Turkey.}
    
    \cvpub{\textbf{Aktepe, S.C.} \& Yet, B. (May 2022). Lexical-relatedness, not conservativity, predicts learning difficulty of quantifiers, 8th International Symposium on Brain and Cognitive Science, Koç University, İstanbul, Turkey.}

    \cvpub{\textbf{Aktepe, S.C.} (April 2019). The acquisition of inverse scope by Turkish L2 learners of English, 13th Student Linguistics Conference, Ankara University, Ankara, Turkey.}
    
    \cvpub{\textbf{Aktepe, S.C.}, (March 2019). The awareness levels of pre-service English language teachers in foreign language education department, The 5th Annual ELT Undergraduate Students Conference, Sakarya University, Sakarya, Turkey}
\end{cvpubs}
